---
title: "ELN Naming Application"
author: "Alistair Grevis-James <alistair.grevis-james@csl.com.au>"
date: "25/01/2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
#Adding the libraries
library(shiny)
library(data.tree)
```

```{r, echo=FALSE}
#Creating the Root Node
D831 <- Node$new("D831")
```

```{r, echo=FALSE}
#Creating the Fundamental Technique Nodes

#HPLC
  FundamentalTechnique <- D831$AddChild("High Pressure Liquid Chromatography")
  FundamentalTechnique$tag <- 'HPLC'
    Methodology <- FundamentalTechnique$AddChild("Size Exclusion")
    Methodology$tag <- 'SE'
      Analyte <- Methodology$AddChild("Analyte")
      Analyte$tag <- ("A1")

#Electrophoresis
  FundamentalTechnique <- D831$AddChild("Electrophoresis")
  FundamentalTechnique$tag <- 'EP'
    Methodology <- FundamentalTechnique$AddChild("Size Exclusion")
    Methodology$tag <- 'SE'
      Analyte <- Methodology$AddChild("Analyte")
      Analyte$tag <- ("A1")
      
#Electrophoresis
  FundamentalTechnique <- D831$AddChild("Cell-Based")
  FundamentalTechnique$tag <- 'CB'
    Methodology <- FundamentalTechnique$AddChild("Size Exclusion")
    Methodology$tag <- 'SE'
      Analyte <- Methodology$AddChild("Analyte")
      Analyte$tag <- ("A1")


```

```{r, echo=TRUE}
#Printing the Tree
print(D831)
print(FundamentalTechnique$tag)
```

```{r, echo=TRUE}
#Adding the Projects
projects = c('', 'CSL689', 'CSL312', 'CSL346')
```

```{r, echo=TRUE}
# Create an empty c
techs = c('')
for (node in D831$children)
{ 
  techs <- c(techs, node$name) 
}

#Print list to confirm
print(techs)
```


```{r eruptions, echo=FALSE}
# Define UI for application that draws a histogram
ui <- fluidPage(
   
   # Application title
   titlePanel("App V1"),
   
   # Sidebar with a slider input for number of bins 
   sidebarLayout(
      sidebarPanel(
         dateInput(
           inputId = "date",
           label = "Analysis Date",
           value = Sys.Date(),
           format = "yyyy-mm-dd"
         ),
         selectInput(inputId = "project",
                     label = "Project",
                     choices = projects
         ),
         selectInput(inputId = "technique",
                     label = "Fundamental Technique",
                     choices = techs
         ),
         uiOutput("methodInput"),
         uiOutput("analyteInput"),
         uiOutput("stringInput")
      ),
      # Show a plot of the generated distribution
      mainPanel(
      )
   )
)

# Define server logic required to draw a histogram
server <- function(input, output) {
   
  output$methodInput <- renderUI({
    
    techName = input$technique
    techNode = Navigate(root, techName)
    
    methods <- c('')
    for (node in techNode$children)
    { 
      methods <- c(methods, node$name) 
    }
    
    selectInput(inputId = "method",
                label = "Methodology",
                choices = methods
    )
    
  })
  
  output$analyteInput <- renderUI({
    
    techName = input$technique
    techNode = Navigate(root, techName)
    
    methodName = input$method
    methodNode = Navigate(techNode, methodName)
    
    analytes <- c('')
    for (node in methodNode$children)
    { 
      analytes <- c(analytes, node$name) 
    }
    
    selectInput(inputId = "analyte",
                label = "Analyte",
                choices = analytes
    )
    
  })
  
  output$stringInput <- renderUI({
    
    dateString = format(input$date, format="%Y%m%d")
    project = input$project
    
    techName = input$technique
    techNode = Navigate(root, techName)
    techName = techNode$tag
    
    methodName = input$method
    methodNode = Navigate(techNode, methodName)
    methodName = methodNode$tag
    
    analyteName = input$analyte
    analyteNode = Navigate(methodNode, analyteName)
    analyteName = analyteNode$tag
    
    textInput(inputId = "string",
              label = "Experiment Name",
              value = paste(dateString, project, techName, methodName, analyteName, sep = "_")
    )
  })

}

# Run the application 
shinyApp(ui = ui, server = server)
```



print(root)



This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

#```{r eruptions, echo=FALSE}
#inputPanel(
#  selectInput("n_breaks", label = "Number of bins:",
#             choices = c(10, 20, 35, 50), selected = 20),
#  
#  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
#              min = 0.2, max = 2, value = 1, step = 0.2)
#)
#
#renderPlot({
#  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
#       xlab = "Duration (minutes)", main = "Geyser eruption duration")
#  
#  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
#  lines(dens, col = "blue")
#})
#```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.


In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.
































